---
title: "recogeo"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

recogeo helps reconciling geographies (such as administrative or electoral unit) that might have changed overtime. 

recogeocompares geographies from time 1 (for example $A_1$) with geographies from time 2 (for example $B_2$) and determine if: 

1. Geographies $A_1$ and $B_2$ are the same (if $A_1$ contains $=B_2$ and $B_2$ contains $A_1$).
2. Geographies $A_1$ has been merged into geography $B_2 (if $B_2$ contains $A_1$ but $A_1$ does not contain $=B_2$).
3. Geography $A_1$ has been split into two or more geographies $B_2$, $C_2$, $D_2$, ... ($A_1$ intersects $B_2$, $C_2$, $D_2$, ...).


## Installation

To install:

```{r, echo=TRUE, eval = FALSE}
# Install devtools if not already installed
# install.packages("devtools") 
devtools::install_github("fraba/recogeo")
```

## Usage

```{r, echo = TRUE, message = FALSE}
library(recogeo)
data(polygons, package = "recogeo")
res <- reconcileGeographies(poly_a, poly_b)
```

`reconcileGeographies()` takes two spatial objects (either a `SpatialPolygons` object from sp or a Simple Feature from sf and returns:

```{r, echo = FALSE}
library(knitr)
kable(res[sample(1:nrow(res), 10),], row.names = FALSE)
```

