---
title: "Reconcile geographies"
author: "Francesco Bailo"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
    dev: 'svg'
vignette: >
  %\VignetteIndexEntry{Reconcile geographies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```


# Working example

```{r, echo = TRUE}
library(recogeo)
data(polygons, package = "recogeo")
res <- reconcileGeographies(poly_a, poly_b)
```

The function `reconcileGeographies()` returns a data.frame with three columns:

```{r, echo = FALSE}
library(knitr)
kable(res[sample(1:nrow(res), 10),], row.names = FALSE)
```

The column `type` can take three values: `r unique(res$type)`.

# Reporting on function results

```{r eval=FALSE}
reportReconciledGeographies(res, poly_a, poly_b, output = 'html')
```


# Example data

```{r}
library(ggplot2)
library(gridExtra)
```


In this document we will use polygons of administrative divisions for 2012 and 2018 of a Mexican state. This is a common situation: we want to merge two datasets of demographics reported for differt years and based on slighly different geographies. 

```{r echo = FALSE, fig.width = 7, fig.height = 4}
theme_set(theme_bw() +
            theme(axis.title=element_blank(),
                  axis.text=element_blank(),
                  axis.ticks=element_blank()))
grid.arrange(
ggplot() +
  geom_sf(data=poly_a) +
  labs(title = expression('SpatialObject'[1])),
ggplot() +
  geom_sf(data=poly_b) +
  labs(title = expression('SpatialObject'[2])),
ncol = 2)
```


Geographies, which usually represent some administrative or electoral unit for which data are reported, might have changed from $time_1$ to $time_2$ in any of the two following way:

1. Geographies $A_1$ and $B_2$ are the same (if $A_1$ contains $=B_2$ and $B_2$ contains $A_1$).

```{r, echo = FALSE, fig.width = 7, fig.height = 6}
theme_set(theme_bw() +
            theme(axis.title=element_blank(),
                  axis.text=element_blank(),
                  axis.ticks=element_blank()))
grid.arrange(
  arrangeGrob(
    ggplot() +
      geom_sf(data = st_transform(poly_a[320,], crs = 4326), 
              fill = 'red', colour = 'red', alpha = .5) +
      labs(title = expression('geography A'[1])),
    ggplot() +
      geom_sf(data = st_transform(poly_b[589,], crs = 4326), 
              fill = 'blue', colour = 'blue', alpha = .5) +
      labs(title = expression('geography B'[1])),
    ncol = 2, nrow = 1),
  ggplot() +
    geom_sf(data = st_transform(poly_a[320,], crs = 4326), 
            fill = NA, colour = 'red', alpha = .5) +
    geom_sf(data = st_transform(poly_b[589,], crs = 4326), 
            fill = NA, colour = 'blue', alpha = .5),
  nrow = 2
)
```


2. Geographies $A_1$ has been merged into geography $B_2 (if $B_2$ contains $A_1$ but $A_1$ does not contain $=B_2$).

```{r, echo = FALSE, fig.width = 7, fig.height = 6}

theme_set(theme_bw() +
            theme(axis.title=element_blank(),
                  axis.text=element_blank(),
                  axis.ticks=element_blank()))
grid.arrange(
  arrangeGrob(
    ggplot() +
      geom_sf(data = st_transform(poly_a[85,], crs = 4326), 
              fill = 'red', colour = 'red', alpha = .5) +
      labs(title = expression('geography A'[1])),
    ggplot() +
      geom_sf(data = st_transform(poly_b[60,], crs = 4326), 
              fill = 'blue', colour = 'blue', alpha = .5) +
      labs(title = expression('geography B'[2])),
    ncol = 2, nrow = 1),
  ggplot() +
    geom_sf(data = st_transform(poly_a[85,], crs = 4326), 
            fill = NA, colour = 'red', alpha = .5) +
    geom_sf(data = st_transform(poly_b[60,], crs = 4326), 
            fill = NA, colour = 'blue', alpha = .5),
  nrow = 2
)
```


3. Geography $A_1$ has been split into two or more geographies $B_2$, $C_2$, $D_2$, ... ($A_1$ intersects $B_2$, $C_2$, $D_2$, ...).

```{r, echo = FALSE, fig.width = 7, fig.height = 12}
theme_set(theme_bw() +
            theme(axis.title=element_blank(),
                  axis.text=element_blank(),
                  axis.ticks=element_blank()))
grid.arrange(
  arrangeGrob(
    ggplot() +
      geom_sf(data = st_transform(poly_a[75,], crs = 4326), 
              fill = 'red', colour = 'red', alpha = .5) +
      labs(title = expression('geography A'[1]))),
  arrangeGrob(
    ggplot() +
      geom_sf(data = st_transform(poly_b[99,], crs = 4326), 
              fill = 'blue', colour = 'blue', alpha = .5) +
      labs(title = expression('geography B'[2])),
    ggplot() +
      geom_sf(data = st_transform(poly_b[105,], crs = 4326), 
              fill = 'blue', colour = 'blue', alpha = .5) +
      labs(title = expression('geography C'[2])),
    ncol = 2, nrow = 1),
  ggplot() +
    geom_sf(data = st_transform(poly_a[75,], crs = 4326), 
            fill = NA, colour = 'red', alpha = .5) +
      geom_sf(data = st_transform(poly_b[99,], crs = 4326),
            fill = NA, colour = 'blue', alpha = .5) +
      geom_sf(data = st_transform(poly_b[105,], crs = 4326), 
            fill = NA, colour = 'blue', alpha = .5),
  nrow = 3, heights = c(1,1,1.5)
)
```

# Testing results

```{r}
test_res <- testReconciledGeographies(res, poly_a, poly_b)
kable(test_res[1:10,])
```


